---
title: "NewsSentiment"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
NewsSentiment is an easy-to-use Python library that achieves state-of-the-art 
performance for target-dependent sentiment classification on news articles. 
NewsSentiment uses the currently best performing targeted sentiment classifier 
for news articles. In contrast to regular sentiment classification, targeted 
sentiment classification allows you to provide a target in a sentence. Only for 
this target, the sentiment is then predicted. This is more reliable in many 
cases, as demonstrated by the following simplistic example: "I like Bert, 
but I hate Robert."

We designed NewsSentiment to serve as an easy-to-use wrapper around the
sophisticated GRU-TSC model, which was trained on the NewsMTSC dataset 
consisting of more than 10k labeled sentences sampled from political news 
articles. More information on the dataset and the model can be found here. 
The dataset, the model, and its source code can be viewed in our GitHub 
repository.

# Installation

During the installation process. Python in the version 3.7.9 will be 
downloaded onto your computer. This is necessary since the python package
that NewsSentiment is based on requires a virtual enviroment using python 
3.7.

```{r setup}
library(NewsSentiment)
```
# Target-dependent Sentiment Classification

Note that using NewsSentiment the first time will take a few minutes because it 
needs to download the fine-tuned language model. Please do not abort this 
initial download. Since this is a one-time process, future use of NewsSentiment
will be much faster.
```{r}
#sentiment <- infer_from_text("I like ", "Peter", " but I don't like Robert.")
#print(sentiment[0])
```

